%add acknowledgements here
The work presented in this thesis was made possible due to a number of excellent advisors, mentors, and colleagues I had throughout my five years in Arizona.  I would like to thank:

My advisor, Prof. Feryal \"Ozel for being an outstanding mentor who taught me about high-energy astrophysics and provided guidance, encouragement, and insight throughout my PhD.  I especially appreciate that she allowed me to pursue my own interests during my thesis work.  Not only was Feryal a great scientific mentor, but she has also been a fierce advocate for myself and her other students; I always knew I could count on her to help me through difficult situations, whether they be personal, political, or pandemic-related.  

Prof. Lorenzo Sironi for being willing to take me on as an ``advisee at a distance'' and teaching me about PIC, plasma astrophysics, and computation.  I appreciate Lorenzo's patience with me during times that I know were stressful for him, and also for having me out to Columbia to collaborate in person multiple times, which are some of my fondest academic memories over the last 5 years.

Prof. Dimitrios Psaltis for his expert advice and teaching throughout graduate school.  In addition to teaching me about black holes, statistics, and computation, Dimitrios provided support and encouragement during difficult times and taught me about the importance of open communication and a strong code of ethics when working in collaborations. 

Dr. Chi-Kwan Chan for his seemingly unbounded knowledge of computation, his patience in teaching me about it, and for never making me feel incompetent for asking him basic questions about related topics.
